KidsAIR: Main analysis

### 2020-11-11 main_analysis_primary_models.Rmd
Analysis updates

model_results <- glmer(lrti_events_di ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)

@@

>>>>

model_results <- glmer(lrti_events_di_total ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), 
                       data = analysis_data, family = binomial)

@@

# plot results
tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high)
tidy_results

### 2020-11-11 main_analysis_secondary_models.Rmd
Analysis updates

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Started 28 Oct 2020, Updated 9 Nov 2020"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  #filter(gender == "Female")
  filter(home_sqft_2level == "1500+")

@@

summary(itt_results)
```

@@

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
itt_education_results <- read_rds(paste0(file_path, "Output/itt_education_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_no_age_results <- read_rds(paste0(file_path, "Output/itt_no_age_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_winter2_tidy,
                              itt_income_tidy, itt_education_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_home_tidy, itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT Winter 2", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI events per child-week at risk \n compared to placebo treatment") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Difference in PM2.5 \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER Winter 1",
                                   "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER home only", "ER - age",
                                   "ER outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI cases per IQR increase n\ in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

```{r}
# Run primary model and print results
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial, offset = log_person_time_at_risk)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))

summary(logreg_results)
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Started 28 Oct 2020, Updated 10 Nov 2020"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) 
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

@@

summary(itt_results)

res <- residuals(itt_results, type="deviance")
plot(predict(itt_results), res)
abline(h=0, lty=2)
qqnorm(res)
qqline(res)
halfnorm(residuals(itt_results))
```

@@

```{r}
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
itt_education_results <- read_rds(paste0(file_path, "Output/itt_education_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_no_age_results <- read_rds(paste0(file_path, "Output/itt_no_age_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, 
                              itt_income_tidy, itt_education_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_home_tidy, itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI events per child-week \n at risk compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

# Plot results
itt_pm_plot_estimates <- itt_pm_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", 
                                   "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "Difference in log(PM2.5) \n compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

@@

# Plot results
er_plot_estimates <- er_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ER Primary", "ER Winter 1",
                                   "ER + income", "ER + burn level",
                                   "ER + smoke act", "ER + window act", "ER + door act",
                                   "ER + sweep act", "ER home only", "ER - age",
                                   "ER outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  labs(y = "LRTI cases per IQR \n increase in PM2.5") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "none",
          legend.text = element_text(size = 14, colour = "black")) 
er_plot_estimates

@@

```{r, echo=TRUE}
# Run primary model and print results
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + child_age + 
                       (1 | home:cohort:area), data = analysis_data, 
                       family = binomial)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))

summary(logreg_results)

at_risk_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean(person_time_at_risk, na.rm = TRUE),
            sd(person_time_at_risk, na.rm = TRUE),
            median(person_time_at_risk, na.rm = TRUE))
at_risk_summary
```
